%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
	{\Huge \scshape Ethan Gill} \\ \vspace{4pt}
	\small \raisebox{-0.1\height}\faPhone\ (587) 703-7642 ~
	\href{mailto:gill.ethan123@gmail.com}{
		\raisebox{-0.2\height}\faEnvelope\  \underline{gill.ethan123@gmail.com}
	} ~
	% \href{https://www.linkedin.com/in/ethan-gill-008a00258/}{
	% 	\raisebox{-0.2\height}\faLinkedin\ \underline{Ethan Gill}
	% } ~
	\href{https://github.com/ethangillengg}{
		\raisebox{-0.2\height}\faGithub\ \underline{ethangillengg}
	} ~
	\raisebox{-0.2\height}\faKey\ {4A28 BC3D 2A80 8673 D24F}
	\vspace{-4pt}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, parsep=2pt]
	\resumeItem{\textbf{Languages:} TypeScript, \Csharp, SQL, Go, Python, \Cpp, C, Bash, Rust, Nix, Lua}
	\resumeItem{\textbf{Frameworks:} .NET, Vue.js, EF Core, Node, React, Next.js, Django}
	\resumeItem{\textbf{Tools:} Git, LSP, Docker, CMake, Nix}
	\resumeItem{\textbf{Concepts:} API Design, State Management, Performance Optimization}
	\item{\textbf{Operating Systems:} Linux, Windows}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Calgary}{}
{BSc. Software Engineering}{Calgary, Alberta}
\resumeItemListStart
\resumeItem{Key Coursework: Data Structures and Algorithms, Operating Systems, Web Development, Database Management}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Sunwapta Solutions}{September 2022 -- Present}
{Full Stack Developer}{Calgary, Alberta}
\resumeItemListStart
\resumeItem{Worked with \textbf{Vue} and \textbf{.NET} to create and design solutions to client's unique business problems.}
\resumeItem{Designed \textbf{CI/CD} pipelines to ensure smooth deployment to on-premise servers.}
\resumeItem{Worked on production code used by \textbf{hundreds of thousands} of users in the grocery retail industry.}
\resumeItem{Led development team on best \textbf{coding practices} and \textbf{software design} minimizing technical debt.}
\resumeItem{Integrated various \textbf{business APIs} together to create a cohesive product.}
\resumeItemListEnd

\resumeSubheading
{PulseMedica}{May 2022 -- September 2022}
{Full Stack Developer Intern}{Edmonton, Alberta}
\resumeItemListStart
\resumeItem{Worked with \textbf{React} and \textbf{TypeScript} to design and implement a frontend medical application used by opthamologists for surgical planning.}
\resumeItem{Gained experience with developer processes (AGILE).}
\resumeItem{Peformed automated frontend testing using the \textbf{Vitest} framework.}
\resumeItem{Collaborated and integrated with other teams (ML, electronics).}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Heart Imaging Visualization} $|$ \emph{React, Python, Django}}{Fall 2023 - Winter 2024}
\resumeItemListStart
\resumeItem{Built a web application to visualize data from heart scans for the engineering capstone project.}
\resumeItem{Optimized the heart scan parser, and \textbf{docker} build resulting in \textbf{50x} and \textbf{40x} speedups respectively.}
\resumeItem{Collaborated with team members to improve \textbf{code quality} and minimize \textbf{technical debt}.}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{\href{https://github.com/ethangillengg/virtual-orrery}{Virtual Orrery \faGithub}} $|$ \emph{\Cpp, Vulkan}}{Fall 2023}
\resumeItemListStart
\resumeItem{Designed and implemented a \textbf{3D model} of the sun, earth and moon using the \textbf{C++ Vulkan} API.}
\resumeItem{Used \textbf{linear algebra} and concepts from \textbf{computer graphics} to implement \textbf{ray-tracing}.}
\resumeItem{Added \textbf{shadow casting} and axial/orbital tilt angles to celestial bodies (earth, moon).}
\resumeItemListEnd
\vspace{-13pt}
\resumeProjectHeading
{\textbf{\href{https://github.com/ethangillengg/worm-rs}{Worm-rs  \faGithub}} $|$ \emph{Rust, CLI}}{Fall 2023}
\resumeItemListStart
\resumeItem{Built a \textbf{Rust} implementation of the classic worm game for the console.}
\resumeItem{Learned the fundamentals of \textbf{Rust}, the \textbf{borrow checker}, and \textbf{state management}.}
\resumeItem{Experimented with \textbf{algorithms} for generating a random number of \textbf{n} positions in a 2D space.}
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}

% %-----------Languages-----------
\section{Languages}
\begin{multicols}{2}
	\begin{itemize}[itemsep=0pt, parsep=2pt, label={}, leftmargin=*] % Adjust itemsep and parsep as needed
		\item \cvskill{TypeScript}{5}
		\item \cvskill{\Csharp}{4}
		\item \cvskill{\Cpp}{3}
		\item \cvskill{Go}{4}
		\item \cvskill{Bash}{3}
		\item \cvskill{Rust}{2}
	\end{itemize}
\end{multicols}
\vspace{0pt}

%-----------Hobbies---------------
\section{Hobbies}
\begin{itemize}[leftmargin=0.15in, label={}, parsep=2pt]
	\resumeItem{\textbf{Linux Dotfiles:}
		{I love to tinker and tweak with my Linux setup for my personal machines.}
	}
	\resumeItem{\textbf{Language Learning:}
		{You can often catch me reading Japanese novels on my e-book during weekends.}
	}
\end{itemize}

